---
title: "Description"
author: "Siva"
date: "2023-10-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Supermarket Sales Data Analysis

Supermarket sales data is imported from Kaggle <https://www.kaggle.com>. 
This dataset contains 1000 records of 17 variables. Three branches of supermarkets 
in 3 different cities were observed for the sales, revenue, cost of goods sold 
and gross income for 4 different product lines. Both men and women customer 
purchases either they are members or non-members were recorded with date and 
time. Also, every transaction was identified with unique invoice id.

Categorical variables are branch, city, type of customer, customer gender and kind of product they buy and method of payment. Quantitative variables are cost of single unit, quantity, 5% markup, revenue, cogs (cost of goods sold) and gross income.

## Descriptive Statistics

```{r smdata_summary}
smdata <- read.csv('data/supermarket_sales.csv')
summary(smdata)
```

## Univariate Data Exploration

### Histogram plots 

```{r smdata_histogram, echo=FALSE}
num_cols = data.frame(subset(smdata, select=c(7,10,17)))
par(mfrow = c(1, 3))
invisible(lapply(1:ncol(num_cols), function(i) hist(num_cols[, i],main=names(num_cols)[i])))
```

### Boxplots 

```{r smdata_bp, echo=FALSE}
num_cols = data.frame(subset(smdata, select=c(7,10,14,16,17)))
par(mfrow = c(1, ncol(num_cols)))
invisible(lapply(1:ncol(num_cols), function(i) boxplot(num_cols[, i],main=names(num_cols)[i])))
```

## Categorical Variables Analysis

```{r smdata_catvar}
table(smdata$branch)
table(smdata$city)
table(smdata$customer_type)
table(smdata$gender_customer)
table(smdata$product_line)
table(smdata$payment_method)
```

##  Bivariate Analysis

###	City Vs Product line
```{r smdata_cpl}
library(ggplot2)
pink = c("#fde0dd","#fa9fb5","#c51b8a")

cpl <- ggplot(smdata) + 
  geom_bar(aes(city,fill = city)) +scale_fill_manual(values = c(pink))+
  xlab(NULL) + 
  ylab(NULL)+ facet_wrap(~product_line)+theme_bw()
cpl
```
### Customer Gender Vs Product Line
```{r smdata_cgpl}
blue = c("#deebf7","#9ecae1","#3182bd")
cgpl =  ggplot(smdata) + 
  geom_bar(mapping=aes(city,fill = gender_customer),position="dodge") +
  scale_fill_manual(values = c("#fa9fb5","#9ecae1"))+xlab(NULL) + 
  ylab(NULL)+ facet_wrap(~product_line)+theme_bw()

cgpl
```

### Customer Gender and Product line based on Payment Method
```{r smdata_cgplpm}
gp = ggplot(smdata) + geom_bar(mapping=aes(payment_method,fill = gender_customer),position="dodge") +
  scale_fill_manual(values = c("#fa9fb5","#9ecae1"))+xlab(NULL) + 
  ylab(NULL)+ facet_wrap(~product_line)+theme_bw()

gp
```

## Observations and Conclusions

On observing the supermarket sales data it is found that there are no missing values
in the dataset and outliers had been spotted in revenue, cogs and gross income
variables. Almost male and female customers are in equal proportion. Equal amounts of data were recorded across the three cities, members and non members are almost equal.
The catagories of products were equally proportional.

In Yangon city the sales of electronics and accessories, home and lifestyle goods
was highest. Health, beauty and fashion accessories sales was the least in this city in 2019.

In Naypyitaw city ranks first in the sales of food and beverages and ranks last in 
the sales of sports and travel ( also in home and lifestyle) in the year 2019.

The Mandalay city is just the opposite of Naypyitaw city because it ranks first in 
sales of sports and travel city and ranks last in sales of food and beverages.
Otherwise it catches with Naypyitaw city in the sales of other products.

Yangon city men mostly buy electronics and accessories, food and beverages whereas
women mosly buy home and lifestyle and sports and travel goods.

In Naypyitaw city men mostly buy health, beauty and fashion accessories and women buy food and beverages and fashion accessories.

Mandalay city women buy mostly fashion accessories and men buy health and beauty
goods mostly in 2019.

